Weakly informative observations: identifying the weakest player

### 2020-08-03 inst/loser.Rmd
label chunks and cache the slow ones

```{r}
n <- 6 # number of competitors
H <- hyper2(pnames=letters[1:6])
L <- ggrl(H,letters[2:n],letters[1]) 
length(L)
L[[1]]
L[[2]]
```

@@

```{r}
(ans_unconstrained <- maxp(L,give=TRUE))
```

@@

```{r}
small <- 1e-2  # numerical necessity
ans_constrained <-
maxp(L,startp=c(small*2,rep(small,n-2)),fcm=rbind(c(1,-1,rep(0,n-3))),fcv=0,give=TRUE)
ans_constrained
```

@@

```{r}
like_single_list(indep(equalp(L[[1]])),L)
```

@@

```{r}
qchisq(0.95,1)
```

>>>>

```{r,label=useggrl}
n <- 6 # number of competitors
H <- hyper2(pnames=letters[1:6])
L <- ggrl(H,letters[2:n],letters[1]) 
length(L)
L[[1]]
L[[2]]
```

@@

```{r,label=executemaxp,cache=TRUE}
(ans_unconstrained <- maxp(L,give=TRUE))
```

@@

```{r,label=constrainthething,cache=TRUE}
small <- 1e-2  # numerical necessity
ans_constrained <-
maxp(L,startp=c(small*2,rep(small,n-2)),fcm=rbind(c(1,-1,rep(0,n-3))),fcv=0,give=TRUE)
ans_constrained
```

@@

```{r,label=likesingle}
like_single_list(indep(equalp(L[[1]])),L)
```

@@

```{r,label=useqchis}
qchisq(0.95,1)
```
